Price of Anarchy for Mean Field Games

### 2018-07-17 PoA.tex
editing first case of proposition 6

	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$. Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$. It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$. Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
		\begin{equation*}
		\begin{split}
		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
		&=:c_1.
		\end{split} 
		\end{equation*}
	ToDo setup
	\begin{equation*}
	\begin{split}
		\left| (b_2 + \bar{b}_2) w^{\bar{b}_2}_t \right| &\leq \frac{ \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot\left( \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}-\frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2} \right)}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} } \\
		& \leq \frac{}{0!!!}
	\end{split}
	\end{equation*}

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $\lambda \neq 1$, then
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
    Clearly we have $\lim_{b_1 \to 0}u_t=:u^{0,b_1}_t$, $\lim_{b_1 \to 0}w_t=:w^{0,b_1}_t$, and $\lim_{b_1 \to 0}\eta_t=:\eta^{0,b_1}_t$, where all three limiting processes are bounded. By the assumption on $\lambda$, $u_t \neq w_t$ on a set of positive Lebesgue measure. By the assumption on $\xi$, we have $\lim_{b_1 \to 0} \bar{x}^{MFG}_t=:\bar{x}^{0,b_1,MFG}_t>0,\ \forall t \in [0,T]$ which is also bounded. Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
    \begin{equation*}
        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ \text{and}\ \Delta SC^{0,b_1}>0.
    \end{equation*}
    Since $\eta^{0,b_1}_t$ is bounded, $\lim_{b_1 \to 0}v_t=:v_t^{0,b_1}>0,\ \forall t>0$ which is also bounded. Using equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$. Therefore, $\lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1$.

@@

    Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$. We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
\end{proof}

>>>>

	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$. Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$. It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, $\left| \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-\delta^{\bar{b}_2 \to \infty}\right|< \epsilon$, and $\left| \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-(-\delta^{\bar{b}_2 \to \infty})\right|< \epsilon$ for $\bar{b}_2>\bar{b}_2^*$. Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
		\begin{equation*}
		\begin{split}
		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
		&=:c_1.
		\end{split} 
		\end{equation*}
	ToDo setup
	\begin{equation*}
	\begin{split}
		\left| (b_2 + \bar{b}_2) w^{\bar{b}_2}_t \right| &\leq \frac{ \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot\left( \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}-\frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2} \right)}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} } \\
		& \leq \frac{}{0!!!}
	\end{split}
	\end{equation*}

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $\lambda \neq 1$, then
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By the assumption on $\lambda$, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{b_1,MFG} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{b_1\to 0,MFG}>0.
	\end{equation*}
	Moreover, $\bar{x}_t^{b_1\to 0,MFG}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left| \bar{x}^{b_1,MFG}_t \right| \leq \vert \mathbb{E}(\xi) \vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
    \begin{equation*}
        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ \text{and}\ \Delta SC^{0,b_1}>0.
    \end{equation*}
    Since $\eta^{0,b_1}_t$ is bounded, $\lim_{b_1 \to 0}v_t=:v_t^{0,b_1}>0,\ \forall t>0$ which is also bounded. Using equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$. Therefore, $\lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1$.

@@

    Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$. We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
    ToDo: check that we showed all 4 cases.
\end{proof}
